Fitbit & ET Glasses - Methods

### 2023-10-09 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
update fitbitpaper

# pairwise comparisons
pwc <- 
  pairwise.t.test(df_anova_subset$mean_hr_std, 
                  df_anova_subset$time_span, 
                  p.adjust="holm")
pwc

effect_size_anova <-
  round(sqrt(0.6829502   /(1-0.6829502   )), 2)

# effect size of pairwise comparisons
library(dplyr)
library(rstatix)
effect_size_pwc <-
  df_anova_subset %>%
  cohens_d(mean_hr_std ~ time_span) %>% 
  as.data.frame()

>>>>

# # pairwise comparisons
# pwc <- 
#   pairwise.t.test(df_anova_subset$mean_hr_std, 
#                   df_anova_subset$time_span, 
#                   p.adjust="holm")
# pwc
# 
# 
# # effect size of ANOVA
# EtaSq(df_anova_phase)
# 
# effect_size_anova <-
#   round(sqrt(0.6829502   /(1-0.6829502   )), 2)
# 
# # effect size of pairwise comparisons
# library(dplyr)
# library(rstatix)
# effect_size_pwc <-
#   df_anova_subset %>%
#   cohens_d(mean_hr_std ~ time_span) %>% 
#   as.data.frame()
